---
title: "The Effect of Small-Business Lending and the T1 Leverage Ratio on ROA"
author: "Matt Brigida"
runtime: shiny
output: 
 html_document:
 theme: spacelab
 highlight: haddock
---

The full panel has been filtererd to include only observations where the leverage ratio is between -50% and 150%, and the bank's assets are less than $100 billion.

The model has both firm and time fixed effects ($\alpha_{it}$), and has the following specification.  All independent variables are lagged one year relative to ROA.

\begin{equation}
ROA = \beta_1 (T1\ Lev.\ Ratio) + \beta_2 \frac{Amt.\ SB\ Loans}{TA} + \beta_3 \% \Delta SB\ Loans + \beta_4 \frac{NPA}{TA} + \beta_5 \frac{Deposits}{TA} + \beta_6 (post\ crisis) + \alpha_{it} + \epsilon_{it}
\end{equation}
where *SB* denotes "Small Business", *NPA* denotes "Non-Performing Assets", and *TA* denotes "Total Assets".  *post crisis* is an indicator variable for the years 2012---2015 inclusive.  

<!-- read in the data -->
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(plm)

panelOrig <- readRDS(url("https://github.com/Matt-Brigida/FFIEC_Call_Reports/blob/master/querying_data_and_analysis/analyses/panel_data_analysis/full_panel/ROA_LHS/panel_mdi_ind.rds?raw=true"))

## panelOrig <<- pdata.frame(panelOrig, index = c("IDRSSD", "quarter"), drop.index=TRUE, row.names=TRUE)
panelOrig <- pdata.frame(panelOrig, index = c("IDRSSD", "quarter"), drop.index=TRUE, row.names=TRUE)

panelOrig <- panelOrig[panelOrig$t1_LR_lagged_1_year > -0.5, ]
panelOrig <- panelOrig[panelOrig$t1_LR_lagged_1_year < 1.5, ]

panelOrig <- panelOrig[panelOrig$total_assets_lagged_1_year > 0, ]
panelOrig <- panelOrig[panelOrig$total_assets_lagged_1_year < 100000000, ]

## panel <- panelOrig
```



## Less than $100,000

```{r echo=FALSE, message=FALSE, warning=FALSE}
## first divide into samples by size

smallest_bank <- min(panel$total_assets_lagged_1_year, na.rm = TRUE)
largest_bank <- max(panel$total_assets_lagged_1_year, na.rm = TRUE)

interval_size <- 10000  # this is $10 million
step_size <- 1000  # $1 million

start_lower <- interval_size * 0
start_upper <- interval_size * 1

## initialize coefs
t1_coef <- 0
t1_aa_coef <- 0
t1_his_coef <- 0
total_t1_aa <- 0
total_t1_his <- 0


sb_coef <- 0
sb_aa_coef <- 0
sb_his_coef <- 0
total_sb_aa <- 0
total_sb_his <- 0

## start counter
i <- 1

while (start_upper + step_size * i < largest_bank){

    panel <- panelOrig[panelOrig$total_assets_lagged_1_year > (start_lower + step_size * i), ]
    panel <- panel[panelOrig$total_assets_lagged_1_year < (start_upper + step_size * i), ]

    tryCatch({
        FEmodel1 <- plm(ROA ~  amt_CI_less_100_SB_loans_Delt_lagged_1_year + t1_LR_lagged_1_year + less_100_lagged_SB_loans_TA + NPA_TA + TD_TA + I(post_crisis_ind) + I(black_ind * t1_LR_lagged_1_year) + I(hispanic_ind * t1_LR_lagged_1_year) + I(black_ind * less_100_lagged_SB_loans_TA) + I(hispanic_ind * less_100_lagged_SB_loans_TA), data = panel, model = "within", effect = "twoways")

        result1 <- summary(FEmodel1)

        t1_coef[i] <- result1$coefficients[rownames(result1$coefficients) == "t1_LR_lagged_1_year"][1]
        t1_aa_coef[i] <- result1$coefficients[rownames(result1$coefficients) == "I(black_ind * t1_LR_lagged_1_year)"][1]
        t1_his_coef[i] <- result1$coefficients[rownames(result1$coefficients) == "I(hispanic_ind * t1_LR_lagged_1_year)"][1]

        total_t1_aa[i] <- t1_coef[i] + t1_aa_coef[i]
        total_t1_his[i] <- t1_coef[i] + t1_his_coef[i]


        sb_coef[i] <- result1$coefficients[rownames(result1$coefficients) == "less_100_lagged_SB_loans_TA"][1]
        sb_aa_coef[i] <- result1$coefficients[rownames(result1$coefficients) == "I(black_ind * less_100_lagged_SB_loans_TA)"][1]
        sb_his_coef[i] <- result1$coefficients[rownames(result1$coefficients) == "I(hispanic_ind * less_100_lagged_SB_loans_TA)"][1]

        total_sb_aa[i] <- sb_coef[i] + sb_aa_coef[i]
        total_sb_his[i] <- sb_coef[i] + sb_his_coef[i]
    },
    error = function(cond){return(NA)}
    )

    ## output to see if all is OK
    print(i)
    print(t1_coef[i])
    print(total_t1_aa[i])
    print(total_t1_his[i])

    print(sb_coef[i])
    print(total_sb_aa[i])
    print(total_sb_his[i])

### increment
    i <- i + 1
    
}

## xaxis <- rep(0, length(t1_coef))
xaxis <- 0
for (k in 1:length(t1_coef)){
          xaxis[k] <- interval_size + step_size * (k - 1)
}

plot(t1_coef)
plot(total_t1_aa)
plot(total_t1_his)

plot(sb_coef)
plot(total_sb_aa)
plot(total_sb_his)

saveRDS(xaxis, "./interval_10m_step_1m/xaxis.rds")
saveRDS(t1_coef, "./interval_10m_step_1m/t1_coef.rds")
saveRDS(total_t1_aa, "./interval_10m_step_1m/total_t1_aa.rds")
saveRDS(total_t1_his, "./interval_10m_step_1m/total_t1_his.rds")
saveRDS(sb_coef, "./interval_10m_step_1m/sb_coef.rds")
saveRDS(total_sb_aa, "./interval_10m_step_1m/total_sb_aa.rds")
saveRDS(total_sb_his, "./interval_10m_step_1m/total_sb_his.rds")


```
		

<!---

## $100,000 to $250,000
		
```{r echo=FALSE, message=FALSE, warning=FALSE}
		
FEmodel2 <- plm(ROA ~ amt_CI_100_250_SB_loans_Delt_lagged_1_year + t1_LR_lagged_1_year + X100_250_lagged_SB_loans_TA + NPA_TA + TD_TA + I(post_crisis_ind), data = panel, model = "within", effect = "twoways")

result2 <- summary(FEmodel2) 

```


## $250,000 to $1,000,000

```{r echo=FALSE, message=FALSE, warning=FALSE}
            
FEmodel3 <- plm(ROA ~ amt_CI_250_1000_SB_loans_Delt_lagged_1_year + t1_LR_lagged_1_year + X250_1000_lagged_SB_loans_TA + NPA_TA + TD_TA + I(post_crisis_ind), data = panel, model = "within", effect = "twoways")

result3 <- summary(FEmodel3)

```

-->
